Spitzer, Gaia, and the Potential of the Milky Way

### 2013-10-16 text/paper1/ms.tex
removed video footnotes

\section{Description and test of our algorithm}
\label{sec:method}
With access to 6D information for stars in a tidal
stream, each star becomes a powerful potential
measure by exploiting the fact that the stars must have come from the
same progenitor: if the orbits of the stars and progenitor are integrated 
\emph{backwards} in a a potential that accurately models the Milky Way, the stars
should recombine with the progenitor (imagine watching satellite destruction in ``rewind").\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.767305}} If the potential is incorrect,
the orbits of the stars will diverge from that of the progenitor and
thus will not be recaptured by the satellite system (Figure~\ref{fig:ps_distance}).\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.767306}}

>>>>

\section{Description and test of our algorithm}
\label{sec:method}
With access to 6D information for stars in a tidal
stream, each star becomes a powerful potential
measure by exploiting the fact that the stars must have come from the
same progenitor: if the orbits of the stars and progenitor are integrated 
\emph{backwards} in a a potential that accurately models the Milky Way, the stars
should recombine with the progenitor (imagine watching satellite destruction in ``rewind"). If the potential is incorrect,
the orbits of the stars will diverge from that of the progenitor and
thus will not be recaptured by the satellite system (Figure~\ref{fig:ps_distance}).
